Finite-state morphological transducers for three Kypchak languages

### 2013-10-20 kipchak-lrec-2013/kipchak-paper.tex
blah
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48157 72bbbca6-d526-0410-a7d9-f06f51895060
more
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48158 72bbbca6-d526-0410-a7d9-f06f51895060

In a linguistic sense, these languages have different amounts of influence from other Turkic branches (e.g., moderate Oguz (SE) influence in the Western group, slight Oguz influence in the Northern group) and from Mongolic languages (moderate influence on the Southern group, lighter in the other groups), and all have heavy influence from Persian.

@@

%FIXME: background on how, when, and with what support were developed?
The transducers for these languages

@@

\subsection{Kazakh}
Kazakh is primarily spoken in Kazakhstan, where it is the national language, sharing official status with Russian as an official language.  Large communities of native speakers also exist in China, neighbouring Central-Eurasian republics, and Mongolia.  Estimates of the total number of speakers range from 8 million \citep{ethnologue} to 11 million \citet{encyclopedin} people.

\subsection{Tatar}
Tatar is spoken in and around Tatarstan by approximately 5.4 million people \citep{ethnologue}. It is co-official with Russian in Tatarstan --- a republic within Russia.  A majority of native speakers of both languages are bilingual in Russian. %, and the standard varieties our system FIXMEs are written in Cyrillic.

\subsection{Kumyk}
Kumyk has approximately 430 thousand speakers \cite{ethnologue}

>>>>

In a linguistic sense, these languages have different amounts of influence from other Turkic branches (e.g., moderate Oghuz (SE) influence in the Western group, slight Oghuz influence in the Northern group) and from Mongolic languages (moderate influence on the Southern group, lighter in the other groups), and all have heavy influence from Persian.

@@

%FIXME: brief background on how, when, and with what support were developed?
The transducers for these languages

@@

\subsection{Kazakh}
Kazakh /qɑzɑq/ is spoken primarily in Kazakhstan, where it is the national language, sharing official status with Russian as an official language.  Large communities of native speakers also exist in China, neighbouring Central-Eurasian republics, and Mongolia.  Estimates of the total number of speakers range from 8 million \citep{ethnologue} to 11 million \citep{encyclopedin} people.

\subsection{Tatar}
Tatar /tɑtɑr/ is spoken in and around Tatarstan by approximately 5.4 million people \citep{ethnologue}.  It is co-official with Russian in Tatarstan --- a republic within Russia.  A majority of native speakers of both languages are bilingual in Russian. %, and the standard varieties our system FIXMEs are written in Cyrillic.

\subsection{Kumyk}
Kumyk /qumuq/ is spoken in Dagestan, a Republic of the Russia Federation, where it is co-official with a number of other languages of Dagestan \citep{ethnologue}.  There are approximately 430 thousand speakers \citep{ethnologue}.
